\documentclass[11pt,a4paper]{my_cv}

\begin{document}

\begin{cvheader}
    \cvroad{The Line  Chatuchak-Mochit}
    \cvpostcode{10900 Chatuchak, Bangkok}
    \cvname{Christoph Sitter}
    \cvphone{+66 80 815 32 91}
    \cvemail{christoph.sitter@gmail.com}
\end{cvheader}

\section{Personal Statement}
I'm a highly qualified and enthusiastic systems engineer with a passion for latency critical systems who has 6 years of professional experience designing and implementing complex software systems. I strive to further my skills, knowledge and education while working in an interesting field that allows me to architect as well as implement large scale software systems.

Currently looking for a new role as a hands-on solutions architect where I can utilise my skills designing and implementing large-scale systems and take the next step in my career.


\section{Professional Expertise}
\begin{expertise}
    \expertiseitem[Programming Languages]{C, Java, Lua, Python, C++, JavaScript, SQL, Rust, LateX}
    \expertiseitem[Operating Systems]{RHEL/CentOS/Fedora, Gentoo Linux, Debian/Ubuntu, Mac OS, Windows}
    \expertiseitem[Technologies]{gcc/gdb, llvm/lldb, valgrind, strace, make, Premake, Cmake, OpenSSL, Gradle, vim, tmux, bash, JVM, TensorFlow, scikit-learn, TCP/IP, UDP, HTTP, XML, UML, databases, Docker, Jenkins, Travis CI, Bitcoin, Ethereum, Docker, Kubernetes, gRPC}
    \expertiseitem[Methodologies]{Agile (Scrum, Kanban), Design Patterns, BDD/TDD, CI/CD}
\end{expertise}

\section{Employment}
\workplace{Solutions Architect}{SCB Securities via Caplin Systems Ltd.}{May 2018 - Current}
Looking for a new challenge, I signed up to be the Solutions Architect as well as Technical Lead for a client facing project with a major Thai bank. Building a cross asset retail investment app that integrates with roughly 20 systems, my main responsibilities are to architect the system, supervise development teams as well as implement spikes and production features. In addition to the technical responsibilities I am involved in managing the client relationship and liaise between stakeholders on both sides. Being actively involved in a project of this magnitude has taught me a lot about maintaining a good vendor/client relationships as well as supervising and coordinating a team of 30 engineers to work efficiently.

\workplace{Platform Architect}{Caplin Systems Ltd.}{Dec 2015 - May 2018}
After working on the platform team for a bit over a year I took over as the architect and my main responsibilities were to maintain the platform software stack ($\sim$ 70 products written in C, Java, C\#, Objective-C, JS and Python) for existing customers as well as enhance them based on regulatory changes, technological movement as well as new customer requirements. This led me to conceptualise an entirely new system which is designed to better suit current cloud-hosting requirements while allowing a smooth transition for existing customers.

\workplace{Technical Team Lead}{Caplin Systems Ltd.}{Nov 2014 - Dec 2015}
After joining the companies platform team I took over the technical team lead role. The role included managing the team and sprints, providing technical guidance in C, Java, JNI and Lua to team members as well as implementing new features and finding/fixing bugs in a large legacy codebase. In addition to the daily duties, I worked with the architect on the design of new features and got involved in gathering requirements from customers, on-site as well as over webex conferences.

\workplace{Software Engineer}{Caplin Systems Ltd.}{Feb 2013 - Nov 2014}
I worked with a Scrum team on delivering a securities trading platform to a major Swiss bank. My role was to implement the backend Java components to enable fast instrument search using in-memory databases, real-time price streaming and trading as well as the design and implementation of a watchlist component that exposed an easy to use messaging API for front-end team to integrate integrate with.

\pagebreak
\section{Education}
\education{University College London}{MSc Web Science and Big Data - Distinction}{Sep 2016 - Sep 2017}
\begin{projects}{10em}
    \project[Blockchain ADR]{MSc Dissertation investigating the use of blockchains to create a dispute resolution system that can automatically resolve legal disputes and avoid litigation based  on immutability guarantees provided by the blockchain and smart contracts.}
\end{projects}
\begin{modules}
    \module{Distributed Systems and Security}
    \module{Supervised Learning}
    \module{Applied Machine Learning}
    \module{Machine Vision}
    \module{Statistical NLP}
    \module{Web Economics}
    \module{Information Retrieval}
    \module{Complex Networks and Web}
\end{modules}

%\education{Westminster University London}{Erasmus exchange}{Sep 2012 - Dec 2012}

\education{Alpen-Adria University Klagenfurt}{BSc Informatics - 2:1}{Sep 2009 - Sep 2012}
\begin{projects}{10em}
    \project[VoiCCN]{BSc Dissertation investigating the feasibility of implementing SIP based Voice over IP services on top of Content Centric Networks, in particular an implementation called CCNx}
    \project[CEP/RETE]{Project and Dissertation about using CEP systems, in particular TIBCO Business Events, for the monitoring and control of the automated manufacturing lines at Infineon Technologies.}
    \project[IT Services Website]{Developed a new Website for the Universities IT Services Department based on Drupal.}
\end{projects}
%Bachelor Thesis: Voice over Content Centric Networks (VoCCN) 2,0
%Bachelor Thesis: Erstellung einer neuen ZID Website 4,0
\begin{modules}
    \module{Distributed Systems}
    \module{Operating Systems}
    \module{Compiler Construcion}
    \module{Algorithms and Complexity Theory}
    \module{Selected Topics in Artificial Intelligence}
    \module{Discrete Mathematics}
    \module{Analysis \& Calculus}
    \module{Databases}
    \module{Knowledge Engineering}
    \module{Logic and Logic Programming}
    \module{Software Engineering I \& II}
    \module{Object-oriented Modelling and Implementation}
\end{modules}


\end{document}
